Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-11 paper/main.tex
move a note to be part of a paragraph

\begin{definition} We define the natural transformation \textcolor{artist}{Artist}  \vartist\ as the tuple $(\vindexc, \vchannelc, \vmarkc, \mathcal{\dtotalc},\mathcal{\vtotalc}, \mathcal{\gtotalc})$ where
  \begin{enumerate}
    \item $\vchannelc: \dtotalc \rightarrow \vtotalc$ is a bundle map from data values to the visual variables they are mapped to
    \item $\vmarkc: \sheafc_{\mathcal{\vtotalc} \rightarrow \sheafc_{\mathcal{\vartistc}}$ is a sheaf map that builds a graphic generating function parameterized by the visual variables 
    \item $\vindexc: \gbasec \rightarrow \dbasec$ is a surjective map from the graphic topological base to the data topological base
  \end{enumerate}
\end{definition}
and $\mathcal{\dtotalc}$, $\mathcal{\vtotalc}$, and $\mathcal{\gtotalc}$ are the categorical representations of fiber bundles that model the data, visual variable, and graphic space of the data to visual transformation.

\note{figure out how to format notes} Usage of the bundle directly in an equation or diagram - $\dotal, \vtotal, \gtotal$ - denotes that the function can be evaluated pointwise over $\dbasepoint \in \dbase$. Use of the categorical form -- $\mathcal{\dtotalc}, \mathcal{\vtotalc}, \mathcal{\gtotalc}$ -- denotes that the function is evaluated over an openset object, meaning that the function needs knowledge of both a value over a point and some information about neighboring values.

\begin{equation}
  \label{eq:artist:construction:all}
  \begin{tikzcd}
    \dtotalc \arrow[rr, "\vchannel"] \arrow[rdd, "\pi"'] &         & \dtotalc \arrow[ldd, "\pi"] & \mathcal{\vtotalc}                                                        & Im_{\vmarkc} \subset \gtotalc                     \\
  &         &                             & {} \arrow[r, "\vmarkc"]                                                   & {}                                \\
   & \dbasec &                             & \mathcal{\dbasec} \arrow[uu, "\sheaf_{\vtotalc}"] \arrow[r, "\vindexc^*"] & \mathcal{\gbasec} \arrow[uu, "\sheaf_{\vmarkc}"']
  \end{tikzcd}
\end{equation}

@@

We represent the graphic output as a fiber bundle because it is an abstraction that is generalizable to various output mediums (screens, 3D prints) and types of graphics. In this work, \gtotal\ assumes the the display is an idealized 2D screen and \gsection\ is an abstraction of rendering. For example, \gsection\ can be a specification such as PDF\cite{bienz1993portable}, SVG\cite{quintScalable2003} or an OpenGL scene graph\cite{CarsonOpenGL1997}, or a rendering engine such as Cairo\cite{CairographicsOrg} or AGG\cite{shemanarevAntiGrainGeometry}.

@@

\begin{example}
As illustrated in \autoref{fig:artist:graphic}, 
\end{example}

>>>>

\begin{definition} We define the natural transformation \textcolor{artist}{Artist}  \vartist\ as the tuple $(\vindexc, \vchannelc, \vmarkc, \mathcal{\dtotalc},\mathcal{\vtotalc}, \mathcal{\gtotalc})$ where
  \begin{enumerate}
    \item $\vchannelc: \dtotalc \rightarrow \vtotalc$ is a bundle map from data values to the visual variables they are mapped to
    \item $\vmarkc: \sheafc_{\mathcal{\vtotalc} \rightarrow \sheafc_{\mathcal{\vartistc}}$ is a sheaf map that builds a graphic generating function parameterized by the visual variables 
    \item $\vindexc: \gbasec \rightarrow \dbasec$ is a surjective map from the graphic topological base to the data topological base
  \end{enumerate}
\end{definition}
and $\mathcal{\dtotalc}$, $\mathcal{\vtotalc}$, and $\mathcal{\gtotalc}$ are the categorical representations of fiber bundles that model the data, visual variable, and graphic space of the data to visual transformation.  We construct the artist to have two stages

\begin{equation}
  \label{eq:artist:construction:all}
  \begin{tikzcd}
    \dtotalc \arrow[rr, "\vchannel"] \arrow[rdd, "\pi"'] &         & \dtotalc \arrow[ldd, "\pi"] & \mathcal{\vtotalc}                                                        & Im_{\vmarkc} \subset \gtotalc                     \\
  &         &                             & {} \arrow[r, "\vmarkc"]                                                   & {}                                \\
   & \dbasec &                             & \mathcal{\dbasec} \arrow[uu, "\sheaf_{\vtotalc}"] \arrow[r, "\vindexc^*"] & \mathcal{\gbasec} \arrow[uu, "\sheaf_{\vmarkc}"']
  \end{tikzcd}
\end{equation}
which are the data to visual variable map $\vchannel$ at the bundle level and the visual variable to graphic map $\vmark$ at the sheaf level. Usage of the bundle directly in an equation or diagram - $\dotal, \vtotal, \gtotal$ - denotes that the function can be evaluated pointwise over $\dbasepoint \in \dbase$. Use of the categorical form -- $\mathcal{\dtotalc}, \mathcal{\vtotalc}, \mathcal{\gtotalc}$ -- denotes that the function is evaluated over an openset object, meaning that the function needs knowledge of both a value over a point and some information about neighboring values.

@@

We represent the graphic output as a fiber bundle because it is an abstraction that is generalizable to various output mediums (screens, 3D prints) and types of graphics.

@@

As illustrated in \autoref{fig:artist:graphic}, in this work, \gtotal\ assumes the the display is an idealized 2D screen. \note{include some more about the figure} The graphic section \gsection\ is an abstraction of rendering. For example, \gsection\ can be a specification such as PDF\cite{bienz1993portable}, SVG\cite{quintScalable2003} or an OpenGL scene graph\cite{CarsonOpenGL1997}, or a rendering engine such as Cairo\cite{CairographicsOrg} or AGG\cite{shemanarevAntiGrainGeometry}.
